Proposed Solution

### 2017-01-22 CAV17/secs/eval.tex
scraping fomr github

The errors reported may have a varying impact on the system, ranging from failing to start, runtime crash, or performance degradation.
Since this is a probablistic system, it is also that some errors are false positives, a violation of the rule has no effect on the system.
It it therefore desirable to sort the reported errors in order of severity. 
To achieve this we use the post analysis metric described in Sec.~\ref{sec:ruleorder}.
To estimate the impact of this metric, we track the rank of known true positives with, and without, the augmented rule ordering in Table~\ref{table:order}.

\begin{table}[h]
\centering
\caption{Effect of Post Analysis Rule Ordering for known true positives}
\label{table:order}
\setlength{\tabcolsep}{1em}
\begin{tabular}{|c|c|c|c|}
\hline
{\bf Class of Error} & {\bf Reference} & {\bf Rank w/o} & {\bf Rank w/} \\
\hline
\hline
Order        & Ex.~\ref{ex:order}   & & \\ 
Missing      & Ex.~\ref{ex:miss}    & & \\ 
Type         & Ex.~\ref{ex:type}    & & \\ 
Fine-Grain   & Ex.~\ref{ex:fine}    & & \\ 
Coarse-Grain & Ex.~\ref{ex:coarse}  & & \\ 
\hline
\end{tabular}
\end{table}

>>>>

The errors reported may have a varying impact on the system, ranging from failing to start, runtime crash, or performance degradation.
Since this is a probablistic system, it is also that some errors are false positives, a violation of the rule has no effect on the system.
It it therefore desirable to sort the reported errors in order of severity. 
To achieve this we use the post analysis metric described in Sec.~\ref{sec:ruleorder}.
To estimate the impact of this metric, we track the rank of known true positives with, and without, the augmented rule ordering in Table~\ref{table:order}.
We compare how close the updated rank is compared to the ideal rank, which was calculated by ennan and estimates the potential severity of an error related to those keywords.
Maybe we actually compare measure the distance from the ideal rank, so that a value of 0 is good.

\begin{table}[h]
\centering
\caption{Effect of Post Analysis Rule Ordering for known true positives}
\label{table:order}
\setlength{\tabcolsep}{1em}
\begin{tabular}{|c|c|c|c|c|}
\hline
{\bf Class of Error} & {\bf Reference} & {\bf Rank w/o} & {\bf Rank w/} & {\bf Ideal Rank}\\
\hline
\hline
Order        & Ex.~\ref{ex:order}   & & \\ 
Missing      & Ex.~\ref{ex:miss}    & & \\ 
Type         & Ex.~\ref{ex:type}    & & \\ 
Fine-Grain   & Ex.~\ref{ex:fine}    & & \\ 
Coarse-Grain & Ex.~\ref{ex:coarse}  & & \\ 
\hline
\end{tabular}
\end{table}
